Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States

### 2017-07-06 doc/manuscript/manuscript.Rmd
fix growth and severity

Mycelial growth of each isolate was generated by activating sclerotia according to the method described previously [@matheron1989in-vitro].
These isolates (N = 366) were phenotypically characterized by determining mycelial compatibility group MCG and aggressiveness.
MCG was determined through co-culturing isolates in pairs on PDA plates, where incompatibility of different MCG resulted in formation of a mycelial barrage [@kohn1990mycelial] and isolates belonging to the same MCG did not form a mycelial barrage.
Aggressiveness of each isolate was assessed using a straw test [@petzoldt1996straw; @teran2006modified] that rates necrotic lesion on a scale of 1-9, with ascending numbers assigned for increasing aggressiveness.
DNA was purified from mycelium of each isolate using a Qiagen DNeasy Plant Mini Kit (Qiagen Inc., Valencia, CA) according to the manufacturer's instructions.

>>>>

Mycelial growth of each isolate was generated by activating sclerotia according to the method described previously [@matheron1989in-vitro].
These isolates (N = 366) were phenotypically characterized by determining mycelial compatibility group MCG and aggressiveness.
MCG was determined through co-culturing isolates in pairs on potato-dextrose agar (PDA) plates, where incompatibility of different MCG resulted in formation of a mycelial barrier [@kohn1990mycelial].
Aggressiveness of each isolate was assessed using a straw test that rates necrotic lesion on a scale from 1--9 with increasing aggressiveness [@petzoldt1996straw; @teran2006modified].
DNA was purified from mycelium of each isolate using a Qiagen DNeasy Plant Mini Kit (Qiagen Inc., Valencia, CA) according to the manufacturer's instructions.
